---
title: "Associate Rules-Car Evaluation"
output: html_document
---

In this paper I will present analysis about car evaluation. Data set is from Machine Learning Depository and Has 1728 observations with 7 variables presented below. I will use associated rules algorithm to present probabilities.

```{r message = FALSE, warning = FALSE}
#Libraries
library(arules)
library(arulesViz)
library(colorspace)

#Reading data
cars<-read.csv('cars.csv',header=TRUE,sep=",")
#The factors of variables
str(cars)

#Here is quick summary of the data.
summary(cars)

```

```{r message = FALSE, warning = FALSE, echo=FALSE,include = FALSE}
rules=apriori(cars)
```

```{r message = FALSE, warning = FALSE}
inspect(rules)


```
We see that all variables has the same amount of observations for each factor besides class of the car.
So what makes car unattractive or attractive?

#Hypotesis one: Unattractive car
To test this hypotesis I will use apriori algorithm which produce itemsets and rules. Results below are sorted by confidence.
```{r message = FALSE, warning = FALSE}
rules.by.conf<-sort(rules, by="confidence", decreasing=TRUE) 
inspect(head(rules.by.conf))
```
Confidence tell us the conditional probability of seeing rhs under the condition of lhs. In our case we can confront now one of our hypotesis that we see cars with low safety or which can only have two persons are considered unattractive.
With which feature unattracive car mostly connects?
```{r message = FALSE, warning = FALSE}
rules.unacc<-apriori(cars, parameter=list(supp=0.001,conf = 0.08), 
                     appearance=list(default="rhs",lhs="class=unacc"), control=list(verbose=F)) 
rules.unacc.byconf<-sort(rules.unacc, by="confidence", decreasing=TRUE)
inspect(rules.unacc.byconf[1:15])
```
The unattractive car will mostly have:

* Safety=low

* Persons=2

* Lug_boot=small, med., big

* Safety=med

We see that the our most frequent group has mostly all types of groups of lug_boot.  
Plot belows confirms that cars with low safety are mostly considered as unattractive cars.

```{r message = FALSE, warning = FALSE}
plot(rules, method = "paracoord", control = list(reorder = TRUE))
#Additional plot
plot(rules,method="graph")
```

#Hypotesis two: Very good car
In another way we would consider cars with high safety, low maintenance and which can have 4 or 5 and more persons a attractive car. Is it true? The results below are sorted by confidence

```{r message = FALSE, warning = FALSE}
rules.vgood<-apriori(cars, parameter=list(supp=0.001,conf = 0.08), 
                      appearance=list(default="lhs",rhs="class=vgood"), control=list(verbose=F)) 
rules.vgood.byconf<-sort(rules.vgood, by="confidence", decreasing=TRUE)
inspect(rules.vgood.byconf[1:15])
```
We can tell that in this data set to consider car very good it has to mostly the best features and not even one bad.
In other way if we know thar car is very good with which feature it usually connects?

```{r message = FALSE, warning = FALSE}
rules.vgood<-apriori(cars, parameter=list(supp=0.001,conf = 0.08), 
                      appearance=list(default="rhs",lhs="class=vgood"), control=list(verbose=F)) 
rules.vgood.byconf<-sort(rules.vgood, by="confidence", decreasing=TRUE)
inspect(rules.vgood.byconf[1:15])
```
We see that in every option presented in table have:

* safety=high

* lug_boot=big

* buying=low

* persons=4 or more

So mostly cars with these features are considered as very good.

#Conclusions

We can see that associate rules can be very helpful in defining the relations between variables.
In this research we used data set of cars to show which features define unattractive and very good car.
